```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load key packages
```{r}
library(tidyverse)
library(lubridate)
library(sf)
library(zoo)
library(ggplot2)
library(ggspatial)
```

## Data Filters
```{r}
#quarter_filter <- c("2017 Q1")

# = c("Battles")

# This variable can be changed to filter the types of conflicts included in the analysis
conflicts_filter = c("Battles", "Strategic developments", "Protests", "Violence against civilians", "Explosions/Remote violence", "Riots")
```

## Load and Prepare Price Data
```{r}
Niger_price <- read.csv("https://raw.githubusercontent.com/Syverpet/Spatial_Analysis_of_Food_Prices_and_Conflicts_in_SAHEL/main/Data/Price_Data/with_lat_long/Niger_prices_with_lat_long.csv")

Mali_price <- read.csv("https://raw.githubusercontent.com/Syverpet/Spatial_Analysis_of_Food_Prices_and_Conflicts_in_SAHEL/main/Data/Price_Data/with_lat_long/Mali_prices_with_lat_long.csv")

Burkina_price <- read.csv("https://raw.githubusercontent.com/Syverpet/Spatial_Analysis_of_Food_Prices_and_Conflicts_in_SAHEL/main/Data/Price_Data/with_lat_long/BurkinaF_prices_with_lat_long.csv")


# IN THIS SECTION -  price columns are converted from character to numeric values, data columns are set to a date format ymd (lubridate), and data is filtered by dates 2010-01-01 and 2021-05-01.

Niger_prices1 <- Niger_price %>%
  mutate(X = row_number()) %>%
  mutate(price = as.numeric(price)) %>%
  mutate(date = ymd(date)) %>% filter(date >= as.Date("2010-01-01") & date <= as.Date("2021-05-01")) 

Mali_prices1 <- Mali_price %>%
  mutate(X = row_number()) %>%
  mutate(price = as.numeric(price)) %>%
  mutate(date = dmy(date)) %>% filter(date >= as.Date("2010-01-01") & date <= as.Date("2021-05-01")) 

Burkina_prices1 <- Burkina_price %>%
  mutate(X = row_number()) %>%
  mutate(price = as.numeric(price)) %>%
  mutate(date = ymd(date)) %>% filter(date >= as.Date("2010-01-01") & date <= as.Date("2021-05-01")) %>% arrange(desc(date))


# IN THIS SECTION -  the date columns are converted to a year-month format and two new columns date-related columns are created; a year column and a quarter column.

date_formatting <- function(data_frame) {
  
  data_frame <-separate(data_frame, Date2, c("year", "month", "day"), sep = "-", convert=TRUE)
  data_frame2 <- select(data_frame, -c(month, day))
  data_frame3 <- data_frame2 %>% mutate(date = as.yearmon(date, "%Y%m"))
  data_frame4 <- data_frame3 %>% mutate(quarter = as.yearqtr(date, "%Y%m"))

  {
    return(data_frame4)
  }
}

Niger_prices1$Date2 <- Niger_prices1$date
Niger_prices3 <- date_formatting(Niger_prices1)

Mali_prices1$Date2 <- Mali_prices1$date
Mali_prices3 <- date_formatting(Mali_prices1)

Burkina_prices1$Date2 <- Burkina_prices1$date
Burkina_prices3 <- date_formatting(Burkina_prices1)

```

```{r}
# IN THIS SECTION - data is filtered to include only the commodities Maize, Millet, Sorghum. 

## variables for filtering food types:
food <- c("Maize - Retail", "Millet - Retail", "Sorghum - Retail")
food1 <- c("Maize (white) - Retail", "Millet - Retail", "Sorghum (white) - Retail")


Niger_prices4 <- Niger_prices3 %>%  filter(cmname %in% food)

Mali_prices4 <- Mali_prices3 %>% filter(cmname %in% food)

Burkina_prices4 <- Burkina_prices3  %>% filter(cmname %in% food1)


# IN THIS SECTION - monthly records are removed if they either are exact duplicates of other records within the same quarter, market and commodity, or if records are missing within the same quarter, eg. if there are only 2 records in for a single quarter, single market, and single commodity.

remove_nonunique_records <- function(data_frame) {
  data_frame2 <- data_frame %>%
  group_by(quarter, mktname, cmname)
data_frame3 <- data_frame2 %>% mutate(distinct_prices = n_distinct(price))
data_frame4 <- data_frame3[data_frame3$distinct_prices > 2, ] %>% ungroup()
{
  return(data_frame4)
}
}

Niger_prices5 <- remove_nonunique_records(Niger_prices4)
Mali_prices5 <- remove_nonunique_records(Mali_prices4)
Burkina_prices5 <- remove_nonunique_records(Burkina_prices4)
```


## Metrics for Food Prices: 
In order to analyse the food prices meaningfully in relation to conflicts we had to aggregate them into a meaningful metric that represents how each market's prices relates to the other markets prices. We chose two different metrics, 1) The mean standard deviation for all prices at each market within each quarter. 2) How each market per quarter deviates in percent from the mean of all prices within that quarter in that country.


### First Food Price Metric:
```{r}
# IN THIS SECTION - A standard deviation of prices are calculated for each commodity, each market, and each quarter is calculated based on min-max normalized prices for each commodity.

# Function for calculating the standard deviation price metric:
calculate_standard_dev <- function(data_frame) {
  data_frame2 <- data_frame  %>%
  group_by(cmname) %>%
  mutate(price_norm = (price - min(price)) / (max(price) - min(price))) %>%
  ungroup()
  
  data_frame3 <- data_frame2 %>%
  group_by(quarter, mktname, cmname) %>% 
  mutate(stdev = sd(price_norm, na.rm =TRUE)) %>%
  ungroup()

  {
    return(data_frame3)
  }
}

Niger_prices6 <- calculate_standard_dev(Niger_prices5)
Mali_prices6 <- calculate_standard_dev(Mali_prices5)
Burkina_prices6 <- calculate_standard_dev(Burkina_prices5)

```

```{r}
# IN THIS SECTION - the mean of the standard deviations for all the crops at each market, per quarter is calculated.

calculate_mean_stdev <- function(data_frame) {
  data_frame2 <- data_frame %>%
  group_by(quarter, mktname) %>%
  mutate(stdev_mean = mean(stdev, na.rm = TRUE)) %>% 
  ungroup()
  {
    return(data_frame2)
  }
}

Niger_prices7 <- calculate_mean_stdev(Niger_prices6)
Mali_prices7 <- calculate_mean_stdev(Mali_prices6)
Burkina_prices7 <- calculate_mean_stdev(Burkina_prices6)
```

```{r}
# IN THIS SECTION - The standard deviation metric for markets situated at the same location are merged. This is to avoid duplicate locations when later doing a spatial join.
merge_same_location_markets <- function(data_frame) {
data_frame2 <- data_frame %>%
  group_by(quarter, lat, long) %>% 
  mutate(stdev_mean = mean(stdev_mean, na.rm =TRUE)) %>%
  ungroup()

{
  return(data_frame2)
}
}

Niger_price8 <- Niger_prices7 #does not have any location markets

Mali_price8 <- merge_same_location_markets(Mali_prices7)

Burkina_price8 <- Burkina_prices7 #does not have any location markets

```

### Second Food Price Metric: for each single quarter for each single market the percent difference from the mean of food prices per country per quarter is calculated.

```{r}
# National Mean-- Price per Quarter and Commodity
mean_diff_column <- function(data_frame) { 
data_frame2<- data_frame %>% 
  group_by(quarter, cmname) %>% 
  mutate(avg_nat_mean= mean(price)) %>%
  ungroup()

data_frame3<- data_frame2%>% 
  group_by(quarter, cmname, mktname) %>% 
  mutate(avg_local_price= mean(price)) %>%
  ungroup()

data_frame4 <-data_frame3 %>% mutate(Percent_Difference = (avg_local_price - avg_nat_mean)/avg_nat_mean*100)

data_frame5<-data_frame4%>%
  group_by(quarter, mktname) %>%
  mutate(avg_difference = mean(Percent_Difference)) %>%
  ungroup()

{
  return(data_frame5)
}
}

Niger_price10 <- mean_diff_column(Niger_price8)
Mali_price10 <- mean_diff_column(Mali_price8)
Burkina_price10 <- mean_diff_column(Burkina_price8)

```

## Load Conflict Data
```{r}
All_conflicts <- read.csv("https://raw.githubusercontent.com/Syverpet/Spatial_Analysis_of_Food_Prices_and_Conflicts_in_SAHEL/main/Data/Conflict_Data/All_Conflict_Events.csv")

Niger_conflicts <- All_conflicts %>%
  select(c(data_id, event_date, event_type, country, latitude, longitude)) %>%
  filter(country == "Niger")

Burkina_conflicts <- All_conflicts %>%
  select(c(data_id, event_date, event_type, country, latitude, longitude)) %>%
  filter(country == "Burkina Faso")

Mali_conflicts <- All_conflicts %>%
  select(c(data_id, event_date, event_type, country, latitude, longitude)) %>%
  filter(country == "Mali") 
```

## Prepare Conflict Data
```{r}
# "add year column" function:

year_column <- function(data_frame) {
  
  data_frame <-separate(data_frame, Date2, c("day","month","year"), sep = " ", convert=TRUE)
  data_frame2 <- select(data_frame, -c(month, day)) 

  {
    return(data_frame2)
  }

}
Niger_conflicts$Date2 = Niger_conflicts$event_date
Niger_conflicts$quarter = Niger_conflicts$event_date
Niger_conflicts2 <- year_column(Niger_conflicts)

Mali_conflicts$Date2 = Mali_conflicts$event_date
Mali_conflicts$quarter = Mali_conflicts$event_date
Mali_conflicts2 <- year_column(Mali_conflicts)

Burkina_conflicts$Date2 = Burkina_conflicts$event_date
Burkina_conflicts$quarter = Burkina_conflicts$event_date
Burkina_conflicts2 <- year_column(Burkina_conflicts)

```

```{r}   
# function for pre_processing the conflict data
Pre_process_conflicts <- function(data_frame) {
  
  data_frame2 <- data_frame %>% mutate(event_date = dmy(event_date)) %>%
  rename("date" = "event_date", "type" = "event_type", "lat" = "latitude", "long" = "longitude") %>% filter(type %in% conflicts_filter)  #%>% filter(date >= as.Date("2019-01-01") & date <= as.Date("2020-01-01"))
  
  data_frame2$date <- as.yearmon(data_frame2$date, "%Y%m")
  data_frame2$quarter <- as.yearqtr(dmy(data_frame2$quarter), "%Y%m")
  
  final_pre_processsed <- data_frame2 %>% arrange(date) #%>% filter(quarter == as.yearqtr(quarter_filter))
  
  {
    return(final_pre_processsed)
  }
}

Niger_conflicts3 <- Pre_process_conflicts(Niger_conflicts2)

Mali_conflicts3 <- Pre_process_conflicts(Mali_conflicts2)

Burkina_conflicts3 <- Pre_process_conflicts(Burkina_conflicts2)

#ggplot(Niger_conflicts3, aes(date, type)) + geom_point() + theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


## Make Simple Feature Geometry Collections from coordinates (for both conflict events and food prices)
```{r}
# Convert Conflict coordinates to WKT and simple features geometry collection:

WKT_conversion_function <- function(data_frame) {
  data_frame$geometry <- paste("POINT(",data_frame$long, ",", data_frame$lat,")")

  data_frame2 <- data_frame %>% mutate(geometry = str_replace_all(geometry, " ", ""))

  data_frame3 <- data_frame2 %>% mutate(geometry = str_replace_all(geometry, ",", " "))  

  {
    return(data_frame3)
  }
}

WKTcol_to_sfc_and_make_sf_collection <- function(data_frame) {
  
  data_frame$geometry <- st_as_sfc(data_frame$geometry)
  final_sf_collection <- st_sf(data_frame, crs = "EPSG:4326")
  {
    return(final_sf_collection)
  }
}

# Convert conflicts geometries
Niger_conflicts4 <- WKT_conversion_function(Niger_conflicts3)
Niger_conflicts5 <- WKTcol_to_sfc_and_make_sf_collection(Niger_conflicts4)

Mali_conflicts4 <- WKT_conversion_function(Mali_conflicts3)
Mali_conflicts5 <- WKTcol_to_sfc_and_make_sf_collection(Mali_conflicts4)

Burkina_conflicts4 <- WKT_conversion_function(Burkina_conflicts3)
Burkina_conflicts5 <- WKTcol_to_sfc_and_make_sf_collection(Burkina_conflicts4)


# Convert prices geometries
Niger_price11 <- WKT_conversion_function(Niger_price10)
Niger_price12 <- WKTcol_to_sfc_and_make_sf_collection(Niger_price11)


Mali_price11 <- WKT_conversion_function(Mali_price10)
Mali_price12 <- WKTcol_to_sfc_and_make_sf_collection(Mali_price11)

Burkina_price11 <- WKT_conversion_function(Burkina_price10)
Burkina_price12 <- WKTcol_to_sfc_and_make_sf_collection(Burkina_price11)

```

## Load Country Boundary Data:
```{r}
Niger_country <- st_read("https://raw.githubusercontent.com/Syverpet/Spatial_Analysis_of_Food_Prices_and_Conflicts_in_SAHEL/main/Data/Country_Boundaries/Niger_boundaries.geojsonl.json")
Mali_country <- st_read("https://raw.githubusercontent.com/Syverpet/Spatial_Analysis_of_Food_Prices_and_Conflicts_in_SAHEL/main/Data/Country_Boundaries/Mali_boundaries.geojsonl.json")
Burkina_country <- st_read("https://raw.githubusercontent.com/Syverpet/Spatial_Analysis_of_Food_Prices_and_Conflicts_in_SAHEL/main/Data/Country_Boundaries/Burkina_boundaries.geojsonl.json")
All_countries <- st_read("https://raw.githubusercontent.com/Syverpet/Spatial_Analysis_of_Food_Prices_and_Conflicts_in_SAHEL/main/Data/Country_Boundaries/All_countries_boundaries.geojsonl.json")

# Plot country boundaries:
All_countries %>% select(ADMIN) %>% plot(reset = FALSE, col = NA, border = "grey", cex = 0.1)
Niger_country %>% select(ADMIN) %>% plot(add = TRUE, col = "blue", border = "grey", cex = 0.1)
Mali_country %>% select(ADMIN) %>% plot(add = TRUE, col = "green", border = "grey", cex = 0.1)
Burkina_country %>% select(ADMIN) %>% plot(add = TRUE, col = "red", border = "grey", cex = 0.1)

 

```


## Exploratory Data Analysis

#### Let's expore the data we have so far. First, let's look at the coundtries of interest:

```{r}
  

ggplot() + 
  
  geom_sf(data = All_countries, fill= "antiquewhite") +
  annotation_scale(location = "br", width_hint = 0.5) + 
  annotation_north_arrow(location = "tl", which_north = "true", pad_x = unit(0.75, "in"), pad_y = unit(0.5, "in"), style = north_arrow_fancy_orienteering) +
  xlab("Longitude") + 
  ylab("Latitude") + 
  ggtitle("Countries of Interest") + 
  theme(plot.title = element_text(size=20, face="bold")) +
  theme(panel.grid.major = element_line(color = gray(.5), linetype = "dashed", size = 0.5), panel.background = element_rect(fill = "aliceblue")) +
  
  annotate(geom = "text", x = -2, y = 18, label = "Mali", fontface = "bold", color = "grey22", size = 4) +
  annotate(geom = "text", x = 10, y = 17, label = "Niger", fontface = "bold",color = "grey22", size = 4) +
  annotate(geom = "text", x = -1, y = 12, label = "Burkina Faso", fontface = "bold", color = "grey22", size = 4)
```
#### As you can see the three countries share long borders with each other which is beneficial in terms of being able to include cross-border effects between the two variables.


#### Now, let's have a look at all the spatial distribution of violent conflict events between 2010-2020:


```{r}
ggplot()  +
  geom_sf(data = All_countries, fill= "antiquewhite") +
  geom_sf(data = rbind(Niger_conflicts5, Mali_conflicts5, Burkina_conflicts5), size=0.3, aes(col = "red")) +
  annotation_scale(location = "br", width_hint = 0.5) + 
  annotation_north_arrow(location = "tl", which_north = "true", pad_x = unit(0.75, "in"), pad_y = unit(0.5, "in"), style = north_arrow_fancy_orienteering) +
  xlab("Longitude") + 
  ylab("Latitude") + 
  ggtitle("Countries of Interest") + 
  theme(plot.title = element_text(size=20, face="bold")) +
  theme(panel.grid.major = element_line(color = gray(.5), linetype = "dashed", size = 0.5), panel.background = element_rect(fill = "aliceblue")) +
  
  scale_color_manual(values=c("red"), labels=c("Conflicts")) + labs(color='Legend') 
```
#### And the spatial distribution of the markets where the food prices have been recorded between 2010-2020:
```{r}
ggplot() + 
  geom_sf(data = All_countries, fill= "antiquewhite") +
  geom_sf(data = rbind(Niger_price12, Mali_price12, Burkina_price12), size=1, aes(col = "navyblue"))+
  annotation_scale(location = "br", width_hint = 0.5) + 
  annotation_north_arrow(location = "tl", which_north = "true", pad_x = unit(0.75, "in"), pad_y = unit(0.5, "in"), style = north_arrow_fancy_orienteering) +
  xlab("Longitude") + 
  ylab("Latitude") + 
  ggtitle("All Markets") + 
  theme(plot.title = element_text(size=20, face="bold")) +
  theme(panel.grid.major = element_line(color = gray(.5), linetype = "dashed", size = 0.5), panel.background = element_rect(fill = "aliceblue")) +
  scale_color_manual(values=c("navyblue"), labels=c("Markets")) + labs(color='Legend')
```


```{r}

# Explore annual std changes:
Niger_mean_quarter <- Niger_price12 %>% group_by(quarter) %>% summarise(stdev_mean = mean(stdev_mean))
Mali_mean_quarter <- Mali_price12 %>% group_by(quarter) %>% summarise(stdev_mean = mean(stdev_mean))
Burkina_mean_quarter <- Burkina_price12 %>% group_by(quarter) %>% summarise(stdev_mean = mean(stdev_mean))
library("plotly")

ggplotly(
ggplot() + 
  geom_line(data= Niger_mean_quarter, aes(y=stdev_mean, x=quarter, col="Niger")) + 
  
  geom_line(data=Mali_mean_quarter, aes(y = stdev_mean, x=quarter,col = "Mali")) + 
  
  geom_line(data= Burkina_mean_quarter, aes(y = stdev_mean, x=quarter,col="Burkina Faso")) + 

  labs(title="Quarterly price standard deviation per country", y="standard deviation of min-max normalised prices", x="quarter", 
       color=NULL) + scale_color_manual(labels = c("Niger", "Burkina Faso", "Mali"), 
                     values = c("Niger"="#00ba38", "Burkina Faso"="#f8766d", "Mali" = "blue")) +
  theme(axis.text.x = element_text( vjust=0.5 , size = 8), plot.title = element_text(size=16, face="bold"))
)
# Quarterly conflicts per country
Niger_quarterly_conflicts2 <- Niger_conflicts3 %>% group_by(quarter) %>% summarise(n_conflicts = n_distinct(data_id))
Mali_quarterly_conflicts2 <- Mali_conflicts3 %>% group_by(quarter) %>% summarise(n_conflicts = n_distinct(data_id))
Burkina_quarterly_conflicts2 <- Burkina_conflicts3 %>% group_by(quarter) %>% summarise(n_conflicts = n_distinct(data_id))


ggplotly(
ggplot() + 
  geom_line(data = Niger_quarterly_conflicts2, aes(x = quarter, y = n_conflicts, col="Niger")) +
  geom_line(data = Burkina_quarterly_conflicts2, aes(x = quarter, y = n_conflicts, col="Burkina Faso")) +
  geom_line(data = Mali_quarterly_conflicts2, aes(x = quarter, y = n_conflicts, col="Mali")) +
  
  labs(title="Quarterly Conflicts per Country", y="number of conflicts", x="quarter", color=NULL) + 
  scale_color_manual(labels = c("Niger", "Burkina Faso", "Mali"), 
                     values = c("Niger"="#00ba38", "Burkina Faso"="#f8766d", "Mali" = "blue")) +
  theme(axis.text.x = element_text( vjust=0.5 , size = 8), plot.title = element_text(size=16, face="bold"))
)
```
## ANALYSIS

### As the analysis is very computionally demanding the option of loading the results from GitHub is given. Hash out the first block and unhash the second to run the full analysis from scratch.

#### 1. Load results of analysis
```{r}
diff_from_mean_correlations <- read.csv("https://raw.githubusercontent.com/Syverpet/Spatial_Analysis_of_Food_Prices_and_Conflicts_in_SAHEL/main/Data/Correlation_Data/diff_from_mean_correlations.csv")

sd_correlations <- read.csv("https://raw.githubusercontent.com/Syverpet/Spatial_Analysis_of_Food_Prices_and_Conflicts_in_SAHEL/main/Data/Correlation_Data/sd_correlations.csv")
```

#### 2. Actual analysis (takes 1 hour + to complete)
```{r}
# suppressPackageStartupMessages(library(spatstat))
# library(stars)
# 
# 
# conflicts_filter_final = c("Battles", "Violence against civilians", "Explosions/Remote violence")
# 
# Niger_conflicts6 <- Niger_conflicts5 %>% filter(type %in% conflicts_filter_final)
# Mali_conflicts6 <- Mali_conflicts5 %>% filter(type %in% conflicts_filter_final)
# Burkina_conflicts6 <- Burkina_conflicts5 %>% filter(type %in% conflicts_filter_final)
# 
# 
# merged_list_margets <- rbind(Niger_price12, Mali_price12, Burkina_price12)
# 
# merged_list_margets2 <- merged_list_margets %>% filter(quarter != "2021 Q1")
# 
# unique_quarters <- c(unique(merged_list_margets2$quarter))
# 
# # All_countries polygons
# All_countries2 <- All_countries %>% st_transform("+init=epsg:3857") %>% select(ADMIN)
# 
# # Bounding Box for All_countries3
# bb <- st_geometry(All_countries2) %>% st_union()
# 
# BW_df <- data.frame()
# 
# 
# 
# # list of bandwidths for the point density maps 
# sigma_list <- list(200000, 150000, 100000, 90000, 80000, 70000, 60000 ,50000, 45000, 40000 ,35000, 30000, 25000, 20000, 15000, 10000, 5000)
# 
# # dataframes for final correlation results per bandwidth
# 
# sd_correlations <- data.frame(bandwidths = c(200000,150000,100000,90000, 80000, 70000, 60000 ,50000, 45000, 40000 ,35000, 30000, 25000, 20000, 15000, 10000, 5000), correlation = NA)
# 
# diff_from_mean_correlations <- data.frame(bandwidths = c(200000,150000,100000,90000, 80000, 70000, 60000 ,50000, 45000, 40000 ,35000, 30000, 25000, 20000, 15000, 10000, 5000), correlation = NA)
# 
# 
# 
# for (bandwidht in sigma_list) {
#   print("bandwidth:")
#   print(bandwidht)
#   
#   for (Q in unique_quarters) {
#     print(Q)
#   
#   
#   # Point data for conflicts for each country
#   Niger_points <- Niger_conflicts6 %>% st_transform("+init=epsg:3857") %>% filter(quarter == Q)
#   Mali_points <- Mali_conflicts6 %>% st_transform("+init=epsg:3857") %>% filter(quarter == Q)
#   Burkina_points <- Burkina_conflicts6 %>% st_transform("+init=epsg:3857") %>% filter(quarter == Q)
#   
#   # Make point_pattern
#   point_patern = c(bb, st_geometry(Niger_points), st_geometry(Mali_points), st_geometry(Burkina_points)) %>% as.ppp()
#   
#   
#   skip_to_next <- FALSE
#   
#     tryCatch(density_map <- density(point_patern, sigma = bandwidht, dimyx = 1000), error = function(e) { skip_to_next <<- TRUE})
#   
#     if(skip_to_next) { next } 
# 
#   density_map_stars <- st_as_stars(density_map) %>% st_set_crs(3857)
#   
#   Niger_price13 <- Niger_price12 %>% filter(quarter == Q)
#   Mali_price13 <- Mali_price12 %>% filter(quarter == Q)
#   Burkina_price13 <- Burkina_price12 %>% filter(quarter == Q)
#   
#   # Market points
#   All_markets_final <- rbind(Niger_price13, Mali_price13, Burkina_price13) %>% st_transform("+init=epsg:3857")
#   
#   # count column
#   All_markets_final$counts <- 1
#   
#   # Aggregate std to one row per mktname/quarter:
#   All_markets_final2 <- All_markets_final %>% group_by(mktname) %>% summarise(final_std = sum(stdev_mean/sum(counts)), final_avg_diff = sum(avg_difference/sum(counts)))
#   
#   # Extract values for each market point from density map:
#   extracted <- st_extract(density_map_stars, All_markets_final2)
#   
#   Final_join <- st_join(All_markets_final2, extracted, join = st_equals)
#   
#   
#   FINAL <- rbind(FINAL, Final_join)
#   
#   print(nrow(FINAL))
#   
#   }
# 
#   sd_correlations[sd_correlations$bandwidths == bandwidht, "correlation"] <- with(na.omit(FINAL), cor(final_std, v))
#   diff_from_mean_correlations[sd_correlations$bandwidths == bandwidht, "correlation"] <- with(na.omit(FINAL), cor(final_avg_diff, v))
#   
#   histo <- FINAL$v
#   hist(histo, breaks = 70)
#   plot(density_map)
#   
#   FINALFINAL <- Final_join[1,1:5]
#   
#   FINAL <- FINALFINAL %>% mutate(final_std = 0) %>% mutate(v = 0) %>% mutate(final_avg_diff = 0)
# }

```

## Final Results and Discussion

#### To visualise the tendency of the relationships between the final correlation coeficients and each used bandwidht we created two scatterplots with a smootihng lines with confidence bands:
```{r}
ggplotly(
ggplot(sd_correlations, aes(x=bandwidths, y= correlation)) +
        geom_smooth()+
        geom_point() +
        ggtitle("Price Standard Deviation vs. Conflict Events")+
        ylab("Correlation coefficients") +
        xlab("Bandwidhts (meters)") +
        theme(plot.title = element_text(size=16, face="bold"))
)
ggplotly(
ggplot(diff_from_mean_correlations, aes(x=bandwidths, y= correlation)) + 
        geom_smooth() +
        geom_point() +
        ggtitle("Price Diff from National Mean vs. Conflict Events")+
        ylab("Correlation coefficients") +
        xlab("Bandwidhts (meters)") +
        theme(plot.title = element_text(size=16, face="bold"))
)
```
#### The results show at smaller bandwitdht distances, between 5 and 35 kilometers there seems to be a correlation between the market price difference from the national mean metric and the conflict event densities. As smaller bandwidhts naturally include fewer points in each kernel, this would allude to that a high density of events within one quarter, happening close to a market, could cause prices to rise above the quarterly national mean.

#### On the other hand the correlation between the price variation or quarterly standard deviation of prices at each market and the conflict event densities shows an opposite relationship, higher correlation at larger bandwidth distances. This being said, the correlation coefficients are much lower than the ones of the deviation from mean metric, which makes this tendency less interesting and as it is more likely to be random.

#### The biggest uncertainty in the results comes from the fact that food prices are most of the time not recorded in markets in very close temporal and spatial proximity to significant violent conflict events. 

#### Another limitation of the conflict event data is that it is based on reports from legacy media and social media content which means it is likely that many conflict events are not recorded as the flow of information is often limited from areas with ongoing violent conflict.

#### In conclusion, the market price difference from the national mean metric shows some promise in having a certain degree of explanatory power over the conflicts, or vice-versa. There is however, as discussed, great uncertainty in regards to how well the data is suited to conduct this analysis. To make stronger claims about these relationships more exploration is needed.
